On the Functionality of the Multilayer Perceptron

### 2020-09-30 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis Draft v0
- Reoranized Sections
- Relabeld important setions
- Appended acknowledgements

@@

\begin{titlepage}
	\begin{center}
   		\vspace*{1cm}
       	\begin{LARGE}
       	\textbf{Classifying Chaotic Synthesizers with a Multimodal Neural Network} \\
       	\end{LARGE}
       	\vspace{1cm}
       	\begin{Large}
       	Thesis Subtitle 
       	\end{Large}             
       	\vspace{1.5cm}

       	\textbf{By: \\ Landon Buell$^1$} \\       
       	\vspace{0.5cm}
       	\textbf{Advised By: \\ Dr. Kevin Short$^2$ , Dr. Maurik Holtrop$^1$} \\
      	\vspace{1cm}
      	A thesis presented for the degree of\\
       	Bachelor of Science in Physics
        \vspace{1cm}

@@

       \vspace{1cm}              
       $^1$Department of Physics and Astronomy\\           
       $^2$Department of Mathematics and Statistics\\
       \vspace{1cm}  
       University of New Hampshire\\
       Durham New Hampshire, USA\\
       Dec 2020\\

   \end{center}
\end{titlepage}

@@

\paragraph*{}In order to train the Multimodal neural network to identify musical instrument sources, we need a suitable data set to present to the model. University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files \textcolor{blue}{Citations!}. These contain short segments of musical instruments performing a single note or a collection of notes in succession.

\paragraph*{}To ensure that these data sets are roughly homogeneous, we read each sample from it's original format, \textit{.aif}, \textit{.mp3}, or similar, and rewrite each sample as a new \textit{.wav} files, sampled at 44.1 kHz, with a 16 bit depth \textcolor{red}{check this!}. This ensures that all data will have a consistent format when features are extracted. We also use this stage to ensure that each audio file has a correct label, and to determine the number of unique output classes.

@@

\paragraph*{}The performance of a neural network is largely dependent of designing an appropriate set of classification features. These are properties of wave forms that can be represented by a numerical value or several numerical values and are used as the primary tool in classification. There are used in place of a full waveform to represent a file's contents We use tools from physics, mathematics, and signal processing to define and explore a comprehensive set of features that enables a high performance of the classifier.

@@

\paragraph*{}With the appropriate set of features designed, and the number of output determined, we can organize the structure of the neural network function. We construct a multimodal neural network than processes two input arrays derived from the same audio sample that share a common label. This network is designed to handle and process each respective input independently, and concatenate the results to produce a single output.

@@

@@

\section{Feature Selections}
\label{sec-FeatureSelections}

\paragraph*{}Even best minds in the world will perform poorly on test which they have studied the wrong material- neural networks are no different. In order to properly train a neural network, the model must be presented with an appropriate set of training input $x$ and a complementary set of training labels $y$ \cite{Geron,Goodfellow,James}. It becomes quickly apparent that the nature of information contained in the input object $x$, called \textit{features}, is \textit{extremely important} to the performance of the classifier. Consider if you were tasked to identify cats and dogs from images, but instead were presented with only the top-most row of pixels- The task would be nearly impossible because of an inappropriate or in complete set of information.

\subsubsection{Audio Preprocessing}

\section{Evaluating Performance}
\label{sec-PerfEval}

@@

\paragraph*{}The confusion matrix (also called a confusion table) is a very quick, often graphical model that can be used to show how a model performs over a subset of predictions. The general idea of this object is count the number of times class $A$ is predicted to be in class $B$, and vice-versa \cite{Geron}. If we see that these classes are being repeatedly \textit{confused} in the model's prediction process, then we must modify the model or features to account for it.

\paragraph*{}For a $k$-classes classifier, a confusion matrix will have shape $k \times k$. Each row represents the actual labeled class and each column represents a predicted class. Thus for a confusion matrix, $C$, we can say that:
\begin{equation}
\label{eqn-ConfMat}
C_{i,j} = 
\text{Number of samples that belong to class $i$, and were predicted to be in class $j$}
\end{equation} 
Thus, $i = j$, represents a correct prediction, and $i \neq k$ indicates an incorrect prediction. A confusion matrix with a strong main diagonal indicates a model that consistently predicts correct labels \cite{Geron}.

\begin{figure}[H]
\label{fig-ConfMat}
\begin{center}
\textcolor{red}{Images of Confusion Matrices Go Here!} 
\end{center}
\caption{Example Confusion Matrices for $k$-classes tasks}
\end{figure}

\paragraph*{}We can also use a confusion matrix to define four useful quantities relating a prediction to it's label. Suppose a prediction, $y^* = p$ and a truth, $y = q$.
\begin{enumerate}
\item \textbf{True-Positive}\\
A sample is a true-positive if $p = q$
\item \textbf{True-Negative}\\

\item \textbf{False-Positive}\\

\item \textbf{False-Negative}\\
\end{enumerate}
\textcolor{red}{finish this!}

@@

@@

>>>>

\setcounter{tocdepth}{2}

@@

\begin{titlepage}
	\begin{center}
   		\vspace*{1cm}
       	\begin{LARGE}
       	\textbf{Classifying Chaotic Synthesizers with a Multimodal Neural Network} \\
       	\end{LARGE}
       	\vspace{1cm}
       	\begin{Large}
       	\textcolor{red}{Thesis Subtitle}
       	\end{Large}             
       	\vspace{1.5cm}

       	\textbf{By: \\ Landon Buell$^1$} \\       
       	\vspace{0.5cm}
       	\textbf{Advised By: \\ Dr. Kevin Short$^2$ , Dr. Maurik Holtrop$^1$} \\
      	\vspace{1cm}
      	A thesis presented for the degree of\\
       	Bachelor of Science in Physics \\
       	\vspace{0.5cm}
       	\textbf{December 2020}
        \vspace{1cm}

@@

       	\vspace{1cm}              
       	$^1$Department of Physics and Astronomy\\           
       	$^2$Department of Mathematics and Statistics\\
       	\vspace{0.5cm}  
       	University of New Hampshire\\
       	Durham New Hampshire, USA\\            
   \end{center}
\end{titlepage}

@@

\paragraph*{}In order to train the Multimodal neural network to identify musical instrument sources, we need a suitable data set to present to the model as training data. University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files \textcolor{blue}{Citations!}. These contain short segments of musical instruments performing a single note or a collection of notes in succession. Each sound file is labeled according to the instrument that is producing that sound.

\paragraph*{}To ensure that these data sets are formatted consistently, we read each sample from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 16 bit depth \textcolor{red}{check this!}. This ensures that all data will have a consistent format when features are extracted. This stage is detailed in sec.(\ref{subsubsec-Preprocessing}).
% ================================================================

@@

\paragraph*{}The performance of a neural network is largely dependent of designing an appropriate set of classification features. These are properties of wave forms that can be represented by a numerical value or several numerical values and are used as the primary tool in classification. We detail these features in sec. (\ref{sec-Features}). These are used in place of a full waveform to represent a file's contents in a low-dimensional array. We use tools from physics, mathematics, and signal processing to define and explore a comprehensive set of features that enables a high performance of the classifier.

@@

\paragraph*{}With the appropriate set of features designed, and the number of output determined, we can organize the structure of the neural network function. We construct a multimodal neural network, explored in sec. (\ref{sec-Architecture}), that processes two input arrays derived from the same audio sample. This network is designed to handle and process each respective input independently, and concatenate the results to produce a single output.

@@

\newpage
\section{Feature Selections}
\label{sec-Features}

\paragraph*{}Audio and Machine learning researchers M. Kashif Saeed Khan and Wasfi G. Al-Khatib discuss the vitality of feature selection \cite{Khan}: \textcolor{red}{I'm not sure how to introduce the importance of feature extraction}
\begin{quote}
The data reduction stage which is also called feature extraction, consists of discovering a few important facts about each class. The choice of features is critical as it greatly affects the accuracy of audio classification. 
\end{quote}
In order to properly train a neural network, the model must be presented with an appropriate set of training input $x$ and a complementary set of training labels $y$ \cite{Geron,Goodfellow,James}. It becomes quickly apparent that the nature of information contained in the input object $x$, called \textit{features}, is \textit{extremely important} to the performance of the classifier. Consider the task of identifying cats and dogs from images, given only images consisting of the top-most row of pixels. The inappropriate choice features does not reflect the significant characteristics of the signal.

\subsubsection{Audio Preprocessing}
\label{subsubsec-Preprocessing}

@@

\newpage
\section{Evaluating Performance}
\label{sec-PerfEval}

@@

\paragraph*{}The confusion matrix (also called a confusion table) is a very quick, often graphical model that can be used to show how a model performs over a subset of predictions. The general idea of this object is count the number of times class $i$ is predicted to be in class $j$, and vice-versa \cite{Geron}. If we see that these classes are being repeatedly \textit{confused} in the model's prediction process, then we must modify the model or features to account for it.

\paragraph*{}For a $k$-classes classifier, a confusion matrix will have shape $k \times k$, and every element is a non-negative integer. Each row represents the "ground truth" or  labeled class, and each column represents a predicted class. Thus for a confusion matrix, $C$, we can say that:
\begin{quote}
\label{eqn-ConfMat}
\begin{center}
$C_{i,j} =$ Number of samples that \\ 
belong to class $i$, and were predicted to be in class $j$
\end{center}

\end{quote}
Thus, indexes where $i = j$ represents a correct prediction, and $i \neq k$ indicates an incorrect prediction. A confusion matrix with relatively large values in main diagonal indicates a model that consistently predicts correct labels \cite{Geron}.

\begin{figure}[H]
\label{fig-ConfMat}
	\begin{subfigure}[h]{0.45\textwidth}
	\begin{center}
	\textcolor{red}{Images of Confusion Matrices Go Here!} 
	\end{center}
	\end{subfigure}
	\begin{subfigure}[h]{0.45\textwidth}
	\begin{center}
	\textcolor{red}{Images of Confusion Matrices Go Here!} 
	\end{center}
	\end{subfigure}
	\begin{subfigure}[h]{0.45\textwidth}
	\begin{center}
	\textcolor{red}{Images of Confusion Matrices Go Here!} 
	\end{center}
	\end{subfigure}
	\begin{subfigure}[h]{0.45\textwidth}
	\begin{center}
	\textcolor{red}{Images of Confusion Matrices Go Here!} 
	\end{center}
	\end{subfigure}
\caption{Example Confusion Matrices for $k$-classes tasks}
\end{figure}

\paragraph*{}We can also use a confusion matrix to define four useful quantities relating a prediction to it's label. Suppose a belongs to class $q$, with the prediction given by, $y^*$ and a label is given by, $y$:
\begin{enumerate}
\item \textbf{True-Positive}\\
A sample is \textit{TP} if $y^* = q$ and $y = q$
\item \textbf{True-Negative}\\
A sample is \textit{TN} if $y^* \neq q$ and $y \neq q$ 
\item \textbf{False-Positive}\\
A sample is \textit{FP} if $y^* = q$ and $y \neq q$ 
\item \textbf{False-Negative}\\
A sample is \textit{FN} if $y^* \neq q$ and $y = q$
\end{enumerate}
\textcolor{red}{Check this!}

@@

\

\subsection{Tracking Metrics over a Period of Training}
\label{subsec-TrainingMetrics}

@@

\item[•]University of Iowa, Electronic Music Studio for a digital sound library ued for training samples

\item[•]Philharmonics Symphony Orchestra for a digital sound library used for training samples
